Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-08-29 manuscript/manuscript.tex
Fixed English error
Add numpy import to second code block in 4.4.3

\begin{lstlisting}[style=python]
from gisttools.gist import load_gist_file
import matplotlib.pyplot as plt
# adapt eww_ref according to the used solvent model!
gist = load_gist_file('gist.dat',
    struct='solute-centered.pdb', eww_ref=-9.533)
bins, (dg, esw, eww, s) = gist.rdf(
    ['A_dens', 'Esw_dens', 'Eww_dens', 'dTSsix_dens'],
    bins=100, rmax=20., normalize='none')
plt.plot(bins, np.cumsum(dg), label='dG')
plt.plot(bins, np.cumsum(eww), label='Eww')
plt.plot(bins, np.cumsum(esw), label='Esw')
plt.plot(bins, np.cumsum(s), label='dS')
\end{lstlisting}

@@

Even though streptavidin-biotin is known to be a very stable complex, the solvation energy favors the dissociation.
This is expected: the binding of biotin to streptavidin is faciliated over a large number of H-bonds and over polar interactions. As such, water is favourably solvates both biotin and streptavidin and an energetic penalty is paid when replacing it during the binding process.

>>>>

\begin{lstlisting}[style=python]
from gisttools.gist import load_gist_file
import matplotlib.pyplot as plt
import numpy as np
# adapt eww_ref according to the used solvent model!
gist = load_gist_file('gist.dat',
    struct='solute-centered.pdb', eww_ref=-9.533)
bins, (dg, esw, eww, s) = gist.rdf(
    ['A_dens', 'Esw_dens', 'Eww_dens', 'dTSsix_dens'],
    bins=100, rmax=20., normalize='none')
plt.plot(bins, np.cumsum(dg), label='dG')
plt.plot(bins, np.cumsum(eww), label='Eww')
plt.plot(bins, np.cumsum(esw), label='Esw')
plt.plot(bins, np.cumsum(s), label='dS')
\end{lstlisting}

@@

Even though streptavidin-biotin is known to be a very stable complex, the solvation energy favors the dissociation.
This is expected: the binding of biotin to streptavidin is faciliated over a large number of H-bonds and over polar interactions. As such, water favourably solvates both biotin and streptavidin and an energetic penalty is paid when displacing it during the binding process.
